### 2021-04-30 submission/manuscript.Rmd
Add code for referring to the number of significant genera shared between tissue compartments

#To Do: Insert code for number of genera different in all 3 types of tissue samples

```
**5-day laxative treatment does not promote more severe CDIs despite altering the mucosal microbiota.** Given the findings from a previous study that demonstrated PEG treatment disrupts the mucus layer and alters the immune response in mice [@Tropini2018], we decided to examine the impact of PEG treatment on the mucosal microbiota and CDI severity. To evaluate the mucosal microbiota, we sequenced snips of tissue collected from the cecum, proximal colon, and distal colon. Similar to what was observed with the stool samples, alpha diversity was lower in the PEG-treated mice compared to clindamycin treatment (Fig. 3A). Although alpha diversity continued to increase over time based on the communities from PEG-treated mice collected at 20 and 30 days post-infection (Fig. 3A, Data Set S1, Sheet X). Group, time point, and their interactions with other variables (cage, experiment number, and sample type) explained the majority of the variation observed in mucosal communities (PERMANOVA combined R^2^ = `r f_d_top_R2_sum_t`, *P* `r format.pval(f_d_top_p_t, eps = 0.05)`, Fig. 3B, Data Set S1, Sheet X). We saw the greatest difference in the mucosal microbiota between treatment groups at 6 days post-infection with 16 genera that were significantly different in all three of the tissue types we collected (cecum, proximal colon, and distal colon; Fig. S3A, Data Set S1, Sheet X). However, at 30 days post-infection only *Bacteroides*, *Clostridiales*, *Firmicutes*, and *Ruminococcaceae* were different between treatment groups and only in the cecum tissues (Fig. 3C, Fig. 2E, Data Set S1, Sheet X). Interestingly, one of the bacteria that was different between treatment groups at 6 days post-infection was *Peptostreptococcaceae* (the genera that contains a sequence that matches *C. difficile*). *Peptostreptococcaceae* was primarily only present in the 5-day PEG treatment group of mice and decreased in the proximal and distal colon tissues over time (Fig. S2B). Thus, PEG treatment had a significant impact on the mucosal microbiota and we detected *C. difficile* sequences in the cecum, proximal colon, and distal colon tissue communities.

>>>>

#Function to find which significant otus/genera/families are shared
intersect_all <- function(a,b,...){
  Reduce(intersect, list(a,b,...))
}
#Number of genera different in all 3 types of tissue samples
kw_genus_cecum <- read_tsv(here("data/process/5_days_PEG_genus_group_cecum.tsv")) %>% 
  filter(p.value.adj < 0.05) %>% pull(genus)
kw_genus_proximal_colon <- read_tsv(here("data/process/5_days_PEG_genus_group_proximal_colon.tsv")) %>% 
  filter(p.value.adj < 0.05) %>% pull(genus)
kw_genus_distal_colon <-  read_tsv(here("data/process/5_days_PEG_genus_group_distal_colon.tsv")) %>% 
  filter(p.value.adj < 0.05) %>% pull(genus)
# of shared genera with significantly different relative abundances between groups
shared_tissue_genera <- length(intersect_all(kw_genus_cecum, kw_genus_proximal_colon, kw_genus_distal_colon))

```
**5-day laxative treatment does not promote more severe CDIs despite altering the mucosal microbiota.** Given the findings from a previous study that demonstrated PEG treatment disrupts the mucus layer and alters the immune response in mice [@Tropini2018], we decided to examine the impact of PEG treatment on the mucosal microbiota and CDI severity. To evaluate the mucosal microbiota, we sequenced snips of tissue collected from the cecum, proximal colon, and distal colon. Similar to what was observed with the stool samples, alpha diversity was lower in the PEG-treated mice compared to clindamycin treatment (Fig. 3A). Although alpha diversity continued to increase over time based on the communities from PEG-treated mice collected at 20 and 30 days post-infection (Fig. 3A, Data Set S1, Sheet X). Group, time point, and their interactions with other variables (cage, experiment number, and sample type) explained the majority of the variation observed in mucosal communities (PERMANOVA combined R^2^ = `r f_d_top_R2_sum_t`, *P* `r format.pval(f_d_top_p_t, eps = 0.05)`, Fig. 3B, Data Set S1, Sheet X). We saw the greatest difference in the mucosal microbiota between treatment groups at 6 days post-infection with `r shared_tissue_genera` genera that were significantly different in all three of the tissue types we collected (cecum, proximal colon, and distal colon; Fig. S3A, Data Set S1, Sheet X). However, at 30 days post-infection only *Bacteroides*, *Clostridiales*, *Firmicutes*, and *Ruminococcaceae* were different between treatment groups and only in the cecum tissues (Fig. 3C, Fig. 2E, Data Set S1, Sheet X). Interestingly, one of the bacteria that was different between treatment groups at 6 days post-infection was *Peptostreptococcaceae* (the genera that contains a sequence that matches *C. difficile*). *Peptostreptococcaceae* was primarily only present in the 5-day PEG treatment group of mice and decreased in the proximal and distal colon tissues over time (Fig. S2B). Thus, PEG treatment had a significant impact on the mucosal microbiota and we detected *C. difficile* sequences in the cecum, proximal colon, and distal colon tissue communities.
